Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-24 manuscript/manuscript.tex
More changes in abstract

\begin{summary}
We present a new methodology to compute the gravitational fields generated by 
any tesseroid whose density varies continuously in depth, i.e. a forward 
gravity model in spherical coordinates for varying densities on the radial 
direction.
It numerical approximates these gravitational fields through the 
Gauss-Legendre Quadrature along with two discretization algorithms that 
increase its accuracy by subdividing the tesseroid into smaller ones.
The first one is a preexisting adaptive discretization algorithm that reduces 
the errors due to the distance between the tesseroid and the computation 
point, while being regulated by a predefined scalar called distance-size ratio 
($D)$.
The second one, controlled by a predefined delta ratio ($\delta$), is a new 
density-based discretization algorithm that decreases the errors introduced by 
the variation of the density function.
We have also obtained analytical solutions for a spherical shell with variable 
density and compared them with the results of the numerical model in case of a 
linear and an exponential density function.
These comparisons allowed to obtain default values for the distance-size and 
the delta ratio in order to guarantee the accuracy of the forward model.
The resulting optimal values of $D$ for the gravity potential, the components 
of its gradient and the Marussi tensor components are 1, 2 and 8, 
respectively.
While a $\delta=0.2$ is needed for the computation of the gravitational 
potential and its gradient components and a $\delta=0.01$ must be used for 
the Marussi tensor components in order to guarantee the accuracy even for high 
varying exponential densities.
We have finally tested this new methodology by modelling the Neuqu\'en 
sedimentary basin, located to the east of the Andes between 32$^\circ$S and 
40$^\circ$S latitude, assigning an exponential density variation to it and 
computing all the gravitational fields it generates.
\end{summary}

>>>>

\begin{summary}
We present a new methodology to compute the gravitational fields generated by 
any tesseroid whose density varies continuously in depth, i.e. a forward 
gravity model in spherical coordinates for varying densities on the radial 
direction.
It numerical approximates these gravitational fields through the 
Gauss-Legendre Quadrature along with two discretization algorithms that 
increase its accuracy by subdividing the tesseroid into smaller ones.
The first one is a preexisting adaptive discretization algorithm that reduces 
the errors due to the distance between the tesseroid and the computation 
point.
While the second one  is a new density-based discretization algorithm that 
decreases the errors introduced by the variation of the density function.
The amount of discretizations made by each algorithm is indirectly controlled 
by two predefined scalar values: the distance-size ratio $D$ for the former 
and the delta ratio $\delta$ for the latter.
We have also obtained analytical solutions for a spherical shell with variable 
density and compared them with the results of the numerical model in case of a 
linear and an exponential density function.
These comparisons allowed to obtain default values for the distance-size and 
the delta ratio in order to guarantee the accuracy of the forward model.
The resulting optimal values of $D$ for the gravity potential, the components 
of its gradient and the Marussi tensor components are 1, 2 and 8, 
respectively.
While a $\delta=0.2$ is needed for the computation of the gravitational 
potential and its gradient components and a $\delta=0.01$ must be used for 
the Marussi tensor components.
We have finally tested this new methodology by modelling the Neuqu\'en 
sedimentary basin, located to the east of the Andes between 32$^\circ$S and 
40$^\circ$S latitude, assigning an exponential density variation to it and 
computing all the gravitational fields it generates.
\end{summary}
